---
title: "NK_Cells_Prediction"
author: "Kalyan Srivastava"
date: "3/25/2021"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)

library(caret)
library(skimr)
library(mlbench)
library(caretEnsemble)


```

## R Markdown


```{r cars}

```

## Let us import the files and do a quick visual analysis. Notice that how the dictribution is either right or lrf skewed. This is still a normal distribution except that it is skewed. This dat could still be used for predictions.

You can also embed plots, for example:

```{r pressure, echo=FALSE}
NKcellDF <- read.csv('/home/srivastava/Documents/NK_Cells.csv')

head(NKcellDF, n=2)
summary(NKcellDF)
skimmed <- skim(NKcellDF)
skimmed
```
```{r , echo=FALSE}
x <- ncol(NKcellDF)
dataset <- NKcellDF[,2:x]
# create a list of 80% of the rows in the originaldataset we can use for
dataset$Status <- factor(dataset$Status)
validation_index <- createDataPartition(dataset$Status,p=0.80, list=FALSE)
# select 20% of the data for validation
testSet<- dataset[-validation_index,]
# use the remaining 80% of data to training and testingthe models
trainSet <- dataset[validation_index,]

levels(factor(dataset$Status))
```
```{r , echo=FALSE}
control <- trainControl(method="cv", number=10)
metriX <- "Accuracy"

set.seed(7)
modelSvmradial <- train(Status~., data=dataset, method="svmRadial", trControl=control)
set.seed(7)
modelLvq <- train(Status~., data=dataset, method="lvq", trControl=control)
set.seed(7)
modelRF <- train(Status~., data=dataset, method="rf", trControl=control)
set.seed(7)
modelRda <- train(Status~., data=dataset, method="rda", trControl=control)
set.seed(7)
modelAda <- train(Status~., data=dataset, method="ada", trControl=control)
set.seed(7)
modelLmt <- train(Status~., data=dataset, method="LMT", trControl=control)
set.seed(7)
modelLda <- train(Status~., data=dataset, method="lda", trControl=control)
results <- resamples(list(ADA=modelLAda, LVQ=modelLvq, RF=modelRF, SVM=modelSvmradial, RDA=modelRda, PLR=modelPlr))

summary(results)
```
```{r , echo=FALSE}
results <- resamples(models)
summary(results)
#generate the numbers from your models
dotplot(results)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
